\LARGE \bf IMU-based pose-estimation for spherical robots with limited resources

### 2021-05-30 mfi21/ieeeconf/root.tex
added prototype pictures

The same experiment was performed with added slide, i.e., more translation than just the rotation would produce.
Here the results shown in Figure \ref{LTestSlide} were not as reliably good as with the slip experiment.
This is due to the timing of the acceleration. In order to recognize the acceleration as translation, the rotation needs to be above a certain threshold, as the algorithm does not allow any translation without rotation at all.
The translation is computed using the accelerometer via double integration.
Therefore the acceleration of the slide movement needs to be at the same time as a minimal amount of rotation. 
If the rotation starts after the sliding, the double integration of the acceleration is suppressed.
When the rotation starts and the translation could be double integrated, it is already zero as the velocity is constant.
This can be seen in Figure \ref{LTestSlide} where the one side of the L was interpreted exactly as long as the pure integration, i.e., approx. 50 cm, and therefore the slide was not recognized, and the other part was correctly interpreted longer than just the integration and with 1.02 m as long as the actual trajectory.
This is to be blamed on the execution of the experiment, as it was not perfectly ensured only to start sliding with ongoing rotation, which is hard to achieve when manually guiding a sphere.
However, the sliding behavior in a real environment could be in both ways, too, so sliding while rolling and starting sliding before rolling.
With slip, this is not a problem, as, by definition, the translation cannot begin before the rotation when slipping.
If so, it would be sliding.
\begin{figure}
\includegraphics[width=\linewidth]{./graphics/LTestSlide.eps}
\caption{X-Y-Position by integration of rotation and the fusion algorithm. An L-shape with 1 meter by 1 meter was performed with provoked slide(translateion without rotation)}
\label{LTestSlide}
\end{figure}
The experiments for sliding did not reliably detect the slide event and, on some occasions, interpreted the distance as shorter than just the integration, as the acceleration of the linear motion was missed.
However, the deceleration of the sphere was still recognized while rotation existed, and therefore, the sphere miscalculated a couple of centimeters.

>>>>

The same experiment was performed with added slide, i.e., more translation than just the rotation would produce.
Here the results shown in Figure \ref{LTestSlide} were not as reliably good as with the slip experiment.
This is due to the timing of the acceleration. In order to recognize the acceleration as translation, the rotation needs to be above a certain threshold, as the algorithm does not allow any translation without rotation at all.
The translation is computed using the accelerometer via double integration.
Therefore the acceleration of the slide movement needs to be at the same time as a minimal amount of rotation. 
If the rotation starts after the sliding, the double integration of the acceleration is suppressed.
When the rotation starts and the translation could be double integrated, it is already zero as the velocity is constant.
This can be seen in Figure \ref{LTestSlide} where the one side of the L was interpreted exactly as long as the pure integration, i.e., approx. 50 cm, and therefore the slide was not recognized, and the other part was correctly interpreted longer than just the integration and with 1.02 m as long as the actual trajectory.
This is to be blamed on the execution of the experiment, as it was not perfectly ensured only to start sliding with ongoing rotation, which is hard to achieve when manually guiding a sphere.
However, the sliding behavior in a real environment could be in both ways, too, so sliding while rolling and starting sliding before rolling.
With slip, this is not a problem, as, by definition, the translation cannot begin before the rotation when slipping.
If so, it would be sliding.
\begin{figure}
\includegraphics[width=\linewidth]{./graphics/LTestSlide.eps}
\caption{X-Y-Position by integration of rotation and the fusion algorithm. An L-shape with 1 meter by 1 meter was performed with provoked slide(translateion without rotation)}
\label{LTestSlide}
\end{figure}
The experiments for sliding did not reliably detect the slide event and, on some occasions, interpreted the distance as shorter than just the integration, as the acceleration of the linear motion was missed.
However, the deceleration of the sphere was still recognized while rotation existed, and therefore, the sphere miscalculated a couple of centimeters.
To test the algorithm in a real spherical robot with working laserscanners, the prototype shown in Figure \ref{fig:prototype}
was build.
The Plate in the middle is equal to the one used to perform the position evaluation.
The IMUs and the micrococontroller are at the exact same position inside the sphere.
The Livox Lidar-Mid-100 laser-scanner was mounted under the plate and the battery above it.
Due to the lack of a locomotion-system, the sphere needs to be rolled externally.

\begin{figure}
\includegraphics[width=\linewidth]{./graphics/photoReal1.jpeg}
\includegraphics[width=\linewidth]{./graphics/photoReal2.jpeg}
\caption{Prototype to test algorithm in envisaged technical environment.}
\label{fig:prototype}
\end{figure}

%TODO Fabian, put input of laserscanns here
